Diagnostic scripts

### 2021-08-02 diagnostics/DiagnosticPlotExamples.Rmd
cross reference full knitted docs

Usage examples (from msSurveysTest.Rmd)

@@

>>>>

Usage examples (from https://github.com/sgaichas/poseidon-dev/blob/master/msSurveysTest.Rmd, see [visualization](https://sgaichas.github.io/poseidon-dev/msSurveysTest.html))

@@

From https://github.com/sgaichas/poseidon-dev/blob/master/SurveyDietCompTest.Rmd, see [visualizations](https://sgaichas.github.io/poseidon-dev/SurveyDietCompTest.html)
